Study locations

### 2022-12-22 Scripts/Map_study_locations.Rmd
Edit on Maurer metadata
edits on map

---
title: "Study locations"
output:
  html_document: default
  pdf_document: default
---

@@

# Plot
g <- ggplot() +
geom_sf(data = cntries, fill = "grey80", color = NA) +
xlim(c(2200000, 7150000)) +
ylim(c(1380000, 5500000)) +
theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue"),
panel.border = element_rect(colour = "black", fill=NA, size=1)) +
geom_sf(data = data_coord, aes(color=Study_id), size = 0.8, stroke = 0, shape = 16) +
theme(legend.position="none") + 
scale_colour_manual(name = "Study \n locations", values = colors)

>>>>

---
title: "Study locations"
output:
  pdf_document: default
  html_document: default
---

@@

# Plot
g <- ggplot() +
geom_sf(data = cntries, fill = "grey85", color = "grey60",size = 0.1) +
xlim(c(2200000, 7150000)) +
ylim(c(1380000, 5500000)) +
theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
size = 0.5), panel.background = element_rect(fill = "aliceblue"),
panel.border = element_rect(colour = "black", fill=NA, size=1)) +
geom_sf(data = data_coord, aes(color=Study_id), size = 0.8, stroke = 0, shape = 16) +
theme(legend.position="none") + 
scale_colour_manual(name = "Study \n locations", values = colors)
